% CMITS - Configuration Management for Information Technology Systems
% Based on <https://github.com/afseo/cmits>.
% Copyright 2015 Jared Jennings <mailto:jjennings@fastmail.fm>.
%
% Licensed under the Apache License, Version 2.0 (the "License");
% you may not use this file except in compliance with the License.
% You may obtain a copy of the License at
%
%    http://www.apache.org/licenses/LICENSE-2.0
%
% Unless required by applicable law or agreed to in writing, software
% distributed under the License is distributed on an "AS IS" BASIS,
% WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
% See the License for the specific language governing permissions and
% limitations under the License.
\section{Manual Mac compliance}
\label{ManualMac}

Being a UNIX-based operating system, Mac OS X can be configured for
compliance programmatically in many cases, and compliance with many
requirements levied by the Mac OS X STIG is in fact automated by this
policy. But some requirements are not automatable as written because they
require human judgment, and for some settings, the effort it would take to
programmatically set them is not worth the return. ``Patches gratefully
accepted,'' as they say.

For these requirements and settings, administrators must comply manually.

\dinkus

\doneby{admins}{macosxstig}{OSX00010 M6}%
\doneby{admins}{mlionstig}{OSX8-00-01165}%
Do not install unnecessary packages on a Mac.

\doneby{admins}{macosxstig}{OSX00015 M6}%
Do not call the administrator account on a Mac something easy to guess,
like ``Administrator,'' or the hostname of the Mac.

\doneby{admins}{macosxstig}{OSX00055 M6}%
Keep all application software on Macs current with security patches and
hotfixes. For Apple-distributed applications, the Apple Software Updater
does this. Other applications must also be kept current.

\doneby{admins}{macosxstig}{OSX00670 M6}%
\doneby{admins}{mlionstig}{OSX8-00-01265}%
Keep the operating system up to date on Macs, as done with the Apple
Software Updater.

\doneby{admins}{macosxstig}{OSX00295 M6,OSX00300 M6}%
Disable guest logon and guest access to shared folders on Macs.

This is done by unchecking the appropriately labelled checkbox found when
the Guest user is chosen in the Accounts section of System Preferences.

\doneby{admins}{mlionstig}{OSX8-00-00110,OSX8-00-00115}%
Do not create temporary or emergency accounts. (This is a trivial
fulfillment of the STIG requirements. If these account types are
necessary, admins must create and apply policies to ensure their
timely expiration.)


\doneby{admins}{macosxstig}{OSX00430 M6}%
Make Macs require administrator authentication to unlock each System
Preference pane.

This is done by checking the appropriately labelled checkbox found in the
General tab of the Security section of System Preferences.

\doneby{admins}{macosxstig}{OSX00475 M6,OSX00480 M6,OSX00485 M6}%
\doneby{admins}{macosxstig}{OSX00490 M6,OSX00495 M6,OSX00500 M6}%
\doneby{admins}{macosxstig}{OSX00505 M6,OSX00510 M6}%
Turn off Screen Sharing, File Sharing, Printer Sharing, Web Sharing,
Remote Login, Remote Management (Apple Remote Desktop), Remote Apple
Events, and Xgrid Sharing on Macs.

This is done by unchecking the appropriately labelled checkboxes found in
the Sharing section of System Preferences.

\doneby{admins}{macosxstig}{OSX00675 M6}%
Maintain ``system recovery backups'' for Macs as required by the STIG.

The contingency backups that can be made
using~\S\ref{module_contingency_backup} may form a large part of your
system recovery backup. If you avoid modifying Macs except using this
\CMITSPolicy\, you can rest assured that your ``emergency system recovery
data'' has ``been updated following the last system modification.''

See the following sections for more requirements binding on you as a
Mac administrator:
\begin{itemize}
\item \S\ref{module_single_user} (\nameref{module_single_user})
\end{itemize}
